---
title: "DATA_SCIENCE-INTERN"
author: "sudhan_maharjan"
date: "January 30, 2019"
output: html_document
---

Forecasting Sentiments

#Get the data from github

```{r}
#getting the csv data from github
tweets <- read.csv("https://raw.githubusercontent.com/maharjansudhan/DATA_SCIENCE_INTERNSHIP/master/Tweets.csv", header=TRUE, sep=",")

head(tweets)
```

```{r}
summary(tweets$airline_sentiment)
```
There are around 9178 negative sentiments passengers have expressed when they were travelling where are around 2363 passengers expressed positive feedbacks and about 3099 passengers expressed neutral sentiments.

It seems like people love to write or express the negative thoughts more than the positive ones.

```{r}
#VIEW THE DATA AND CREATE NAMES
str(tweets)
```

```{r}
#to check how many candidates were there
library(dplyr)
count(tweets, vars = "name")

total_airline <- length(unique(tweets$airline))
total_airline

```

There are total 14640 passengers who expressed their sentiments when they were travelling on these 6 different airlines.

```{r}
#to see how many of the participants expressed sentiments
library(ggplot2)
qplot(airline_sentiment, data = tweets, fill = airline_sentiment, ylab="Sentiments") + theme(axis.text.x = element_text(angle=60, vjust=0.6))

```



```{r}
negative_sentiment <- tweets %>% 
  select(airline_sentiment, airline)

```

```{r}
#to see how many of the participants expressed Reasons for negative feedback
library(ggplot2)
qplot(negativereason, data = tweets, fill = negativereason, ylab="Reason") + theme(axis.text.x = element_text(angle=60, vjust=0.6))

```



More than 5500 passengers were didn't want to participate in giving any feedbacks. But mostly people gave negative feedback because they experienced a bad customer service, their luggages were misplaced, they had a late flight, and so on.

```{r}
#to see airlines with most negative feedback
library(ggplot2)
ggplot(tweets, aes(x = airline_sentiment, fill = airline_sentiment)) +
  geom_bar() + facet_grid(. ~ airline) + theme(axis.text.x = element_text(angle=60, vjust=0.6),
       plot.margin = unit(c(4,0,4,0), "cm"))

```

The airlines with most negative feedbacks are United Airlines, US Airways, and Ameircan Airlines respectively.

